intro

### 2021-10-04 06_Paper/ER-ED/intro.Rmd
added text

Das ist nur eine Test-Intro

>>>>

# 1. Introduction

[...]
Individual subjective values of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

## Adapting an effort discounting paradigm

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, variing reward.
